A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 subarchitectures/planner.sa/trunk/src/latex/AAAI11/evaluation.tex
active is no longer a word

We have implemented our switching approach in the MAPSIM
environment~\cite{brenner:nebel:jaamas09},
using \system{dlib-ml}~\cite{king:2009} for belief
revision. Sequential sessions use a modified version of Fast
Downward~\cite{fast-downward}, and DT sessions use our own contingent
procedure. We also implemented a simple dual-mode replanning {\em
baseline} approach. Here, when a switching action is scheduled for
execution the DT session applies a single entropy reduction action,
whose execution can provide evidence regarding the truth value of an
active assumption.
%%
%%  -- i.e,. we say a fact can
%% be directly sensed, if there is a DTPDDL {\em sense} declaration that
%% mentions the fact in its precondition. 
%%
Control is then immediately
returned to a new sequential session.

>>>>

We have implemented our switching approach in the MAPSIM
environment~\cite{brenner:nebel:jaamas09},
using \system{dlib-ml}~\cite{king:2009} for belief
revision. Sequential sessions use a modified version of Fast
Downward~\cite{fast-downward}, and DT sessions use our own contingent
procedure. We also implemented a simple dual-mode replanning {\em
baseline} approach. Here, when a switching action is scheduled for
execution the DT session applies a single entropy reduction action,
whose execution can provide evidence regarding the truth value of an
{\em relevant} assumption.
%%
%%  -- i.e,. we say a fact can
%% be directly sensed, if there is a DTPDDL {\em sense} declaration that
%% mentions the fact in its precondition. 
%%
Control is then immediately
returned to a new sequential session.

### 2011-02-09 subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
active is no longer a word

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a
small positive (negative) numeric quantity which captures
the utility the agent receives for correctly (incorrectly) rejecting
an assumption.
%%
In terms of action physics, a disconfirm action can only be executed
once, and otherwise is modelled as self-transformation.
%%
We only consider {\em relevant} assumptions when constructing the
abstract model.  If \switchAction\ is the action that switched the
system to a DT session, then an assumption $\assumptiveS{i}$ is {\em
relevant} if it is necessary for the outcome of \switchAction\ to be
determined.  Continuing our simplified example, if the trace is:

@@

In order to guarantee fast DT sessions, planning occurs for a small
abstract problem. In our setting, where the underlying decision
process has a deterministic action model, a significant cause of
problem largeness is due to the number of states that occur with
non-zero probability in the underlying belief-state. In posing a small
abstract process for a DT session, we construct an abstract
belief-state that is chiefly characterised by facts related to the
current trace. In that abstraction, instances of operator or sense
declarations whose specification mentions an excluded fact are not
available.
%%
In detail, we first construct an $(\pp{:init})$ declaration which
contains the root term, and relevant assumptions from the trace --
e.g., (Fig.\ref{fig:abstraction-b}) gives an example fragment, where
diamonds are probabilistic terms, and circles are atomic and/or
conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure until the belief space size
reaches a predefined limit (Fig.\ref{fig:abstraction-c}).

>>>>

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a
small positive (negative) numeric quantity which captures
the utility the agent receives for correctly (incorrectly) rejecting
an assumption.
%%
In terms of action physics, a disconfirm action can only be executed
once, and otherwise is modelled as a self-transformation.
%%
We only consider {\em relevant} assumptions when constructing the
abstract model.  If \switchAction\ is the action that switched the
system to a DT session, then an assumption $\assumptiveS{i}$ is {\em
relevant} if it is necessary for the outcome of \switchAction\ to be
determined.  Continuing our simplified example, if the trace is:

@@

In order to guarantee fast DT sessions, planning occurs for a small
abstract problem. In our setting, where the underlying decision
process has a deterministic action model, a significant cause of
problem largeness is due to the number of states that occur with
non-zero probability in the underlying belief-state. In posing a small
abstract process for a DT session, we construct an abstract
belief-state that is chiefly characterised by facts related to the
current trace. In that abstraction, instances of operator or sense
declarations whose specification mentions an excluded fact are not
available.
%%
In detail, we first construct an $(\pp{:init})$ declaration which
contains the root term, and relevant assumptions from the trace --
e.g., (Fig.\ref{fig:abstraction-b}) gives an example fragment, where
diamonds are probabilistic terms, and circles are atomic and/or
conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the {\em
relevant}
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure until the belief space size
reaches a predefined limit (Fig.\ref{fig:abstraction-c}).
